### 2023-03-08 manuscript.tex
Updating the comparison table [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/454ea98fc5bad08fda4ba675c377a7db51d7a419.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/454ea98fc5bad08fda4ba675c377a7db51d7a419/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367442220

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb}{SORTEE-Github-Hackathon/manuscript@1ca2ca7}
on March 8, 2023.

@@

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/454ea98fc5bad08fda4ba675c377a7db51d7a419/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/454ea98fc5bad08fda4ba675c377a7db51d7a419}{SORTEE-Github-Hackathon/manuscript@454ea98}
on March 8, 2023.

@@

  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0674}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0567}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0301}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0390}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0408}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0567}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2039}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1844}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2855}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0355}}@{}}
\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\label{tbl:compare}\tabularnewline
Cloud-storage backup
Does it provide a reasonably unrestrictive free version?
Is it permanent (e.g.~through a DOI)?
Cloud-storage backup
Does it provide a reasonably unrestrictive free version?
Is it permanent (e.g.~through a DOI)?
Multi-tool & GitHub & Yes & Yes & Yes & No & Broadly used free version. Advanced features are provided for free to students and education professionals. & A DOI can only be obtained when integrating to other services that can mint a DOI (e.g., Zenodo, OSF). & 100 MB per file, 500 MB per private repository (2 GB for paid accounts). 100 GB for public repositories. Larger files (up to 2 GB) can be attached to releases. & Not applicable. \\
Multi-tool & Open Science Framework & Yes & Yes & Yes & Yes & Yes. & Yes & 25 GB for private projects, up to 5 GB per file, plus partner add-ons, 50 GB for public projects & Yes \\
Long-term (public) data repositories & PANGAEA & Yes & Yes & Yes & No & Yes. & Yes & 10 GB free & No \\
Long-term (public) data repositories & Zenodo & After published & After published & Yes & No & Yes. & Yes & 50 GB per dataset & Yes \\
Long-term (public) data repositories & Dryad & After published & After published & Yes & No & No, however certain journals cover costs. & Yes & 300 GB per publication & No. \\
Long-term (public) data repositories & Figshare & Yes & Yes & Yes & No & Yes. & Yes & 20 GB free, up to 5 TB & Yes \\
Temporary (personal) drive storage & Google Drive & Yes & Yes & Yes & Yes & Free version is restrictive. & No & 15GB free, up to 100GB with Google One & Yes \\
Temporary (personal) drive storage & Box & Limited & Yes & Yes & Yes & No. & No & UnLimited total size for subscription & Yes \\
Temporary (personal) drive storage & DropBox & Limited & Yes & Yes & Yes & Free version is restrictive. & No & 2 GB free & Yes \\
Temporary (personal) drive storage & OneDrive and the Office Suite & Yes & Yes & Yes & Yes & Free version is restrictive. & No & 5 GB free, up to 1TB paid & Yes \\
Collaborative code and text editors & Overleaf (online latex editor) & Yes & Yes & Yes & Yes & Free version is restrictive. Only affiliated institutions (majority from the Global North) obtain premium access. & No & 1 MB for individual LaTeX files, 50MB for individual files, unlimited project size. & Yes \\
Collaborative code and text editors & Jupyter Notebook & Yes & Yes & Yes & With Colab & Yes. & No & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & Yes \\
Collaborative code and text editors & HackMD & Yes & Yes & Yes & Yes & Free version is moderatively restrictive. & No & 3 documents free, private invitee limits & Yes \\
Collaborative code and text editors & Colaboratory & Yes & Yes & Yes & Yes & Free version is moderatively unresitrcitve, unless high computational resources are required. & No & Colab that is free of charge notebooks can run for at most 12 hours. File storage is bounded to Google Drive's limitations. 12 GB GPU RAM . & No. \\
